### 2020-05-06 system-model.tex
:construction: Frequency-selective IRS

		\begin{subsubsection}{Frequency-Flat IRS}
			In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
			\begin{equation}
				\begin{split}
					\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2
					&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}\\
					&=\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})
				\end{split}
			\end{equation}
			where $t$ is an auxiliary variable with unit modulus and
			\begin{equation}
				\boldsymbol{R}=
				\begin{bmatrix}
					\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & \boldsymbol{\Phi}_n{h_{D,n}} \\
					h_{D,n}^*{\boldsymbol{\Phi}_n^H}         & h_{D,n}^*{h_{D,n}}
				\end{bmatrix},
				\quad \bar{\boldsymbol{v}}=\
				\begin{bmatrix}
					\boldsymbol{v} \\
					t
				\end{bmatrix},
				\quad \bar{\boldsymbol{V}}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H
			\end{equation}
			Hence, \ref{op:1} is transformed to
			\begin{maxi}
				{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
				\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho)\ge{\bar{z}}}
				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
				\addConstraint{\boldsymbol{V}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
			\end{maxi}
			To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.

			The phase optimization subproblem is formed as follows. For a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:temp3} reduces to
			\begin{maxi}
				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
				\addConstraint{z(\boldsymbol{V})\ge{\bar{z}}}
				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
				\addConstraint{\boldsymbol{V}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
			\end{maxi}

@@

		% ? AO: optimize phase shifts with given weights
		Define waveform matrices $\boldsymbol{M}_I=\boldsymbol{w}_I^*\boldsymbol{w}_I^T$ and $\boldsymbol{M}_P=\boldsymbol{w}_P^*\boldsymbol{w}_P^T$. Also, let $\boldsymbol{M}_{I/P, n}$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and nulls the remaining entries. It holds that $\boldsymbol{M}_{I/P,0} \succeq 0$ and $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$ for $n{\ne}0$ \cite{Huang2017}. Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_phase}.
		\begin{figure*}[b]
			\hrule
			\begin{equation}\label{eq:z_k_phase}
				\begin{split}
					z
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})\\
					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^H+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^H}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
				\end{split}
			\end{equation}
		\end{figure*}

>>>>

		\begin{subsubsection}{Frequency-Flat IRS}
			In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
			\begin{equation}
				\begin{split}
					\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2
					&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}\\
					&=\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})
				\end{split}
			\end{equation}
			where $t$ is an auxiliary variable with unit modulus and
			\begin{equation}
				\boldsymbol{R}_n=
				\begin{bmatrix}
					\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & \boldsymbol{\Phi}_n{h_{D,n}} \\
					h_{D,n}^*{\boldsymbol{\Phi}_n^H}         & h_{D,n}^*{h_{D,n}}
				\end{bmatrix},
				\quad \bar{\boldsymbol{v}}=\
				\begin{bmatrix}
					\boldsymbol{v} \\
					t
				\end{bmatrix},
				\quad \bar{\boldsymbol{V}}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H
			\end{equation}
			Hence, \ref{op:1} is transformed to
			\begin{maxi}
				{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
				\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
				\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{V},\rho)\ge{\bar{z}}}
				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
				\addConstraint{\boldsymbol{V}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
			\end{maxi}
			To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.

			% ? AO: optimize phase shifts with given waveform
			The phase optimization subproblem is formed as follows. For a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:temp3} reduces to
			\begin{maxi}
				{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
				\addConstraint{z(\boldsymbol{V})\ge{\bar{z}}}
				\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
				\addConstraint{\boldsymbol{V}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{V})=1}
			\end{maxi}
			To tackle the non-convex current constraint, we define waveform matrices $\boldsymbol{M}_{I/P}=\boldsymbol{w}_{I/P}^*\boldsymbol{w}_{I/P}^T$. On top of this, let $\boldsymbol{M}_{I/P, n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and nulls the remaining entries. Therefore, the current expression \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_irs}.
			\begin{figure*}[b]
				\hrule
				\begin{equation}\label{eq:z_k_irs}
					\begin{split}
						z
						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})\\
						% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
						% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^H+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^H}\\
						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
					\end{split}
				\end{equation}
			\end{figure*}
			Introduce auxiliary variables $t_{I/P,n}=\boldsymbol{h}^H\boldsymbol{M}_{I/P,n}\boldsymbol{h}=\mathrm{Tr}()$ and we have $t_{I/P,n}t_{I/P,n}^*=t_{I/P,-n}t_{I/P,-n}^*$ by noticing $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$. Further define $\boldsymbol{t}_{I/P}=[t_{I/P,1},\dots,t_{I/P,N-1}]^T \in \mathbb{C}^{N-1}$.

			% * It holds that $\boldsymbol{M}_{I/P,0} \succeq 0$ and $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$ for $n{\ne}0$.

@@
